Improved Smooth Free-Form Deformation with Sharp Feature Awareness

### 2016-08-15 paper.tex
save 8-15

@@

Thus, the weakness introduced by bad quality triangle(see \ref{fig:clip_quality}) can also be conquered if we ask for a method which can clip model to triangle as regular as possible rather than clip against knot boxes. On the other side, for two triangle which have common edge, our new the clipping scheme should be the same on the common edge to avoid cracks.

\begin{figure}
  \centering
  \subfloat[][]{\includegraphics[width=.45\textwidth]{pic/clip_quality1}}\hfill
  \subfloat[][]{\includegraphics[width=.45\textwidth]{pic/clip_quality2}}\hfill
  \caption{clipping demonstrate}
  \label{fig:clip_quality}
\end{figure}

>>>>

\textcolor{green}{Free-form deformation (FFD\cite{Sederberg86}), as well as many kinds of variants, is useful and widely used whether in academia or in industry when refer to computer graphics and geometric modeling. However, Classic FFD is very simple and efficient but also has many limitation, it is conducted on the sampled points of the geometric model and the approach tends to produce an aliased deformation result when using a low sampling density.}

@@

Thus, the weakness introduced by bad quality triangle(see \ref{fig:clip_quality}) can also be conquered if we ask for a method which can clip model to triangles as regular as possible rather than clip against knot boxes. On the other side, for two triangles which have the common edge, the clipping scheme generated by our clipping method should be the same on the common edge to avoid cracks.

\begin{figure}
  \centering
  \subfloat[][the clipped model's triangle quality]{\includegraphics[width=.45\textwidth]{pic/clip_quality1}}\hfill
  \subfloat[][the original model's triangle quality]{\includegraphics[width=.45\textwidth]{pic/clip_quality2}}\hfill
  \caption{clipping demonstrate}
  \label{fig:clip_quality}
\end{figure}
